Colonies - Compute Continuums across Platforms

### 2023-03-29 paper_2023/paper.tex
wip

This paper presents a framework called Colonies, which is built around a loosely coupled microservices architecture that separates workflow definitions from implementation and deployment. The main objective is to create a tool where monolithic workflows can be broken down into independent and separated compute units that can be dynamically added or removed while executing workflows. These compute units can be implemented in any computer language and be deployed anywhere on the Internet. Ultimately, the Colonies framework facilitates coordination among diverse software systems operating on different platforms in executing unified workflows.

>>>>

This paper presents a framework called Colonies, which is built around a loosely coupled microservices architecture that separates workflow definitions from implementation and deployment. The main objective is to create a tool where monolithic workflows can be broken down into independent and separated compute units that can be dynamically added or removed while executing workflows. These compute units can be implemented in any computer language and be deployed anywhere on the Internet. Ultimately, the Colonies framework facilitates coordination among diverse software components operating on different platforms in executing unified workflows.
